---
title: "R Project 1 - Hello R"
author: "Cassandra Staats"
date: "9/16/2020"
output: 
  html_document: 
    fig_width: 5
    highlight: tango
    theme: sandstone
---


### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```



### Exercise 1

Based on the help file, there are 1,846 rows and 3 columns in the datasaurus_dozen file. 
The 3 variables included in the data frame are the dataset, x-values, and y-values.


```{r}
datasaurus_dozen %>%
  count(dataset) %>%
  print(13)
```



### Exercise 2

Plots the data in the dino dataset:

```{r plot-dino}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


Calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```





### Exercise 3

Plots the data in the star dataset:

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


Evaluate the correlation coefficient between `x` and `y` for the star dataset:

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```


The star dataset compares to the dino dataset by being larger in size. However,
they are very similar. The star data set correlation coefficient is -0.0629611, 
while the dino data set correlation coefficient is -0.06447185, which is just
slightly smaller.






### Exercise 4

Plots the data in the cirle dataset:

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


Evaluate the correlation coefficient between `x` and `y` for the circle dataset:

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```


The circle dataset compares to the dino dataset by being smaller in size. However,
they are very similar. The circle data set correlation coefficient is -0.06834336,
while the dino data set correlation coefficient is -0.06447185, which is just
slightly larger.




### Exercise 5

Plot all datasets at once:

```{r fig.height=8, fig.width=8}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
  theme(legend.position = "none")
```


Calculate all of the datasets summary correlation coefficients:

```{r}
datasaurus_dozen %>%
group_by(dataset) %>%
summarize(r = cor(x, y)) %>%
print(13)
```




